Fast and optimal centroiding of faint stars

### 2015-11-19 ms/figure.tex
more modification

Asymptotically, maximum likelihood estimators can achieve maximum efficiency. That is, for sufficiently large 
number of estimates in a set of maximum likelihood estimates $\{\theta_{\text{ML}}\}$, the root-mean-squared 
error becomes arbitrarily close to the CRLB (see \citet{cramer}; \citet{lecam} for proof).

However, the relation (\ref{inequality}) does not necessarily hold for biased estimators. That is, 
the root-mean-squared-error for a biased estimator can be smaller than the CRLB (see \citet{lecam} for examples).
Therefore, we want to investigate the conditions under which the RMSE arising from a given centroiding method 
becomes close to the CRLB, or whether it can become equal to the CRLB in which case the method is \emph{saturating} 
the bound, or whether it can drop below the CRLB in which case the method is \emph{beating} the bound (and threfore must be biased).

>>>>

Asymptotically, maximum likelihood estimators can achieve maximum efficiency. That is, the RMSE from a 
large set of maximum likelihood estimates $\{\theta_{\text{ML}}\}$, 
becomes greater than or equal to the CRLB (see \citet{cramer}; \citet{lecam} for proof).

However, the relation (\ref{inequality}) does not necessarily hold for biased estimators. That is, 
the root-mean-squared-error for a biased estimator can be smaller than the CRLB (see \citealt{lecam} for examples).
Therefore, we want to investigate the conditions under which the RMSE arising from a given centroiding method 
becomes close to the CRLB, or whether it can become equal to the CRLB in which case the method is \emph{saturating} 
the bound, or whether it can drop below the CRLB in which case the method is \emph{beating} the bound (and threfore must be biased).
